Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2021-06-05 paper/msg.tex
Remove a FIXME.

FIXME THREE IDO REASONS TO CARE: EXPRESS STRONG AND WEAK FORM, DIAGONAL OF IDO UNKNOWN BUT POSITIVE? IN SMOOTHER, SPECTRUM OF IDO DETERMINES STABILITY OF TIME-STEPPING

Now we may re-write \eqref{eq:strongform} more simply as an NCP with a hidden dynamical problem:
\begin{align}
s - b &\ge 0  \label{eq:idostrongform} \\
\Phi(s) - a &\ge 0 \notag \\
(s - b) (\Phi(s) - a) &= 0 \notag
\end{align}
Here the statements hold on all of $\Omega$ and the roles of the data $a,b$ are evident.  The solution is the ice surface $z=s(x,y)$ while the variables $\bu,p$ are hidden within the evaluation of $\Phi(s)$.

>>>>

We will be concerned with three aspects of the IDO:
\renewcommand{\labelenumi}{(\emph{\roman{enumi}})}
\begin{enumerate}
\item Immediately we use $\Phi$ to simplify the SIGP strong form and express its weak form.
\item Section \ref{sec:smoothers} approximates the diagonal entries of the Jacobian $\Phi'$ to construct smoothers.
\item Section \ref{sec:evolution} relates the spectrum of $\Phi'$ to the stability of time-stepping methods.
\end{enumerate}

For (\emph{i}) we re-write \eqref{eq:strongform} as a simpler NCP with a hidden dynamical problem:
\begin{align}
s - b &\ge 0  \label{eq:idostrongform} \\
\Phi(s) - a &\ge 0 \notag \\
(s - b) (\Phi(s) - a) &= 0 \notag
\end{align}
Here the statements hold on all of $\Omega$ and the roles of the data $a,b$ are evident.  The solution is the ice surface $z=s(x,y)$ while the variables $\bu,p$ are hidden within the evaluation of $\Phi(s)$.
